Cartograms with Dynamic Features

### 2022-03-01 paper/section/data.tex
draft: update algorithm and review

Obtaining the data is challenging, especially when an Electronic Health Records (EHR) dataset is involved \cite{wang2021EHRa}. The data acquisition involves multiple steps. The first step is to obtain both geospatial boundaries and EHR data that match one another. The second step is to pre-process the EHR data for removing empty and erroneous values. The final step is to transform the data into a format that is suitable for visualization.

@@

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=0.6\columnwidth]{figure/ccg.png}
    \caption{A map of 106 CCGs in England as of April 2021, obtained from the Open Geography portalx \cite{opengeographyportalxOpen}.}
    \label{fig:ccg}
\end{figure}
}

\subsubsection{Clinical Commissioning Groups}

Clinical Commissioning Groups (CCGs) are the main geographic unit of the National Health Service (NHS) in the UK \cite{nhsNHS}. The number of CCGs changes each year due to the NHS re-organization. The most up-to-date shapefile is available from the Open Geography portalx \cite{opengeographyportalxOpen}. We decided to use the CCG shapefile from 2020 at the time of writing, there is no public EHR data published based on the latest CCG re-organization that took place in April 2021.

\subsubsection{Rivers}

@@

We obtained the Clinical Commissioning Group Outcomes Indicator Set (CCG OIS) from NHS Digital \cite{nhsdigitalClinical}. The OIS is a set of indicators that are used to measure the quality of care and the associated health outcomes in the NHS. Some datasets include:
\begin{itemize}
    \item Under 75 mortality
    \begin{multicols}{2}
        \begin{itemize}
            \item Cardiovascular disease
            \item Respiratory disease
            \item Liver disease
            \item Cancer
        \end{itemize}
    \end{multicols}
    \item Emergency hospital admission
        \begin{itemize}
            \item Stoke
            \item Alcohol-specific admission and readmission
            \item Coronary heart disease
            \item Readmissions within 30 days of discharge
            \item Children with lower respiratory tract infections
        \end{itemize}
\end{itemize}

>>>>

Obtaining the heterogenous data can be challenging, especially when an Electronic Health Records (EHR) dataset is involved \cite{wang2021EHRa}. The data acquisition involves multiple steps. The first step is to obtain both geospatial boundaries and EHR data that match one another. The second step is to pre-process the EHR data to remove empty and erroneous values. The final step is to transform the data into a format that is suitable for visualization.

@@

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=0.6\columnwidth]{figure/ccg.png}
    \caption{A map of 135 CCGs in England as of 2020, obtained from the Open Geography portalx \cite{opengeographyportalxOpen}.}
    \label{fig:ccg}
\end{figure}
}

\subsubsection{Clinical Commissioning Groups Shapefile}

Clinical Commissioning Groups (CCGs) are the main geographic unit of the National Health Service (NHS) in the UK \cite{nhsNHS}. The number of CCGs changes over time due to the NHS re-organization. The most up-to-date shapefile is available from the Open Geography portalx \cite{opengeographyportalxOpen}. We decided to use the CCG shapefile from 2020 at the time of writing, because there is no public EHR data published based on the latest CCG re-organization that took place in 2021.

\subsubsection{River Features}

@@

We obtained the Clinical Commissioning Group Outcomes Indicator Set (CCG OIS) from NHS Digital \cite{nhsdigitalClinical}. The OIS is a set of indicators that are used to measure the quality of care and the associated health outcomes in the NHS. Some datasets include:
\begin{itemize}
    \item Under 75 mortality
    \begin{multicols}{2}
        \begin{itemize}
            \item Cardiovascular disease
            \item Respiratory disease
            \item Liver disease
            \item Cancer
        \end{itemize}
    \end{multicols}
    \item Emergency hospital admission
        \begin{itemize}
            \item Stroke
            \item Alcohol-specific admission and readmission
            \item Coronary heart disease
            \item Readmissions within 30 days of discharge
            \item Children with lower respiratory tract infections
        \end{itemize}
\end{itemize}

### 2022-03-01 paper/section/main.tex
draft: update algorithm and review

\section{\software}

\algoref{alg:UpdateNodePosition} describes the overview of \software. We first load all processed data from \secref{sec:{Data Description}} and apply VPSC \cite{dwyer2006fast} recursively to remove overlaps. We chose VPSC over other node overlap removal algorithms since VPSC is able to provide spread minimization and node movement minimization while maintaining a good level of global shape preservation \cite{chen2020Node}. During each recursion, we check node trajectories (See \algoref{alg:check river crossing}) and move back nodes that crossed a river. A recursion ends when 1) no overlaps are present; 2) no nodes crossed a river. We then increase the node size and repeat the recursion until the entire map canvas is filled.

@@

\begin{algorithm}[tb!]
    \caption{The procedure to update node positions by removing overlaps and prevent nodes from crossing rivers.}\label{alg:UpdateNodePosition}
    \textbf{Variables:} \\
    $NodeList \gets$ a list of nodes representing CCGs \\
    $Node_{size}\gets$ the current size of all nodes \\
    $Node_{inc} \gets$ the increment node size of each iteration \\
    $Node_{max} \gets$ the maximum size of a node \\
    $Node_{stale} \gets$ the maximum number of iterations before a stalemate \\
    \begin{algorithmic}[1]
        \Procedure{UpdateNodePosition}{}
        \While{$ Node_{size} < Node_{max} $}

        \State $ nodeList_{ora} \gets $ RunVPSC ($ NodeList $)

            \For{$ node^i_{ora} \in nodeList_{ora} $}

                \If {MoveNode ($ Node^i, node^i_{ora} $)}
                    \State $ cross \gets $ \Call{CheckRiverCrossing}{$ Node^i, node^i_{ora} $}

                    \If{$ cross = True $}
                        \State $ Node^i.stale \gets Node^i.stale + 1 $

                        \If{$ Node^i.stale < Node_{stale} $}
                            \State \Call{MoveNode}{$ Node^i $}
                        \Else
                            \State \Call{DeriveCorridor}{$ Node^i, node^i_{ora} $}
                        \EndIf

@@

        \State $Node_{size} \gets Node_{size} + Node_{inc}$

@@

\begin{algorithm}[tb!]
    \caption{The procedure to update a node's position.}\label{alg:move position}
    \begin{algorithmic}[1]
        \Procedure{MoveNode}{$ Node, Node_{new} $}
        \If{$ Node.x = Node_{new}.x $ and $ Node.y = Node_{new}.y $}
            \State \Return{$ False $}
        \EndIf

        \State init. $ x,y $

        \If{$ Node_{new}$ is $ undefined $}
            \State $previous \gets Node.history.pop() $
            \State $ x \gets previous.x,~y \gets previous.y $
        \Else
            \State $ x \gets Node_{new}.x,~y \gets Node_{new}.y $
            \State $ Node.history.push(x, y) $
        \EndIf

        \State $ Node.x \gets x $
        \State $ Node.y \gets y $
        \State \Return{$ True $}
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

@@

\subsection{River Cross Checking}

We use rivers as topological boundaries to prevent nodes from crossing them. When a node's position changes, we check if the node's trajectory intersects any segment of a river, see \algoref{alg:check river crossing}. A boundary collision detection is performed to reduce the number of line intersection detections required.

% \begin{noindent}
\begin{algorithm}[tb!]
    \caption{The procedure to check if a node crosses a river.}\label{alg:check river crossing}
    \textbf{Variables:} \\
    $RiverEdges \gets$ a list of river edges formed by two points \\

    \begin{algorithmic}[1]
        \Procedure{CheckRiverCrossing}{$ Node, Node_{ora} $}
            \For{$ edge \in RiverEdges $}
                \State $ node_b \gets $ GenerateBoundary ($ Node, Node_{ora} $)
                \State $ edge_b \gets $ GenerateBoundary ($ edge $)
                \State $ collide \gets $ DetectBoundaryCollision ($ node_b, edge_b $)
                \If{$ collide = True $}
                    \State $ node_l \gets $ GenerateLine ($ Node, Node_{ora} $)
                    \State $ edge_l \gets $ GenerateLine ($ edge $)
                    \State $ intersect \gets $ DetectLineIntersection ($ node_l, edge_l $)
                    \If{$ intersect = True $}
                        \State \Return{$ True $}
                    \EndIf
                \EndIf
            \EndFor
            \State \Return{$ False $}
        \EndProcedure
    \end{algorithmic}
\end{algorithm}
%\end{noindent}

@@

As the VPSC always tries to produce an optimal node layout where node spread and movement are minimized, a node might be repeatedly traveling between two positions due to the lack of available space, creating a stalemate situation for recursions, as shown in \figref{fig:stalemate}. In order to create space for VPSC to generate a new layout, we introduce a user-adjustable parameter, $ Node_{stale} $, to break the stalemate: if a node is traveling between two positions for more than $ Node_{stale} $ iterations, it is considered to be in a stalemate. A stalemate triggers a corridor derivation which moves all nodes within the corridor by $ \mathcal{D} $ set by the user (See \figref{fig:corridor} and \algoref{alg:derive corridor}).

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/stalemate.png}
    \caption{A stalemate situation is when a node repeatedly travels between two positions (A and B) for more than $Node_{stale}$ iterations. }
    \label{fig:stalemate}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/corridor.png}
    \caption{When a stalemate occurs, a corridor (black rectangular) is derived based on the current (A) and previous (B) positions of the node that crossed a river, as described in \algoref{alg:derive corridor}. All nodes within the corridor are moved by $ \mathcal{D} $ in the direction of $ \vec{BA} $. }
    \label{fig:corridor}
\end{figure}
}

@@

\begin{algorithm}[tb!]
    \caption{The procedure to derive a corridor to move included nodes. We use a SVG canvas, where the point of origin (0,0) is located at the top left corner, with the x-axis extending to the right and the y-axis extending to the bottom, there is no negative axes.}\label{alg:derive corridor}
    \textbf{Variables:} \\
    $\mathcal{C}_l \gets$ the length of a corridor \\
    $\mathcal{C}_w \gets$ the width of a corridor \\
    $\mathcal{D} \gets$ the distance to move nodes within the corridor \\
    $Node_{size}\gets$ the current size of all nodes \\
    \begin{algorithmic}[1]
        \Procedure{DeriveCorridor}{$ Node, Node_{old} $}
        \State MoveNode ($ Node $)

        \State $ \Delta x \gets Node.x - Node_{old}.x,~ \Delta y \gets Node.y - Node_{old}.y $

        \State $ slope \gets \frac{\Delta x}{\Delta y}$

        \State $ pLine = $ \Call{DerivePoint}{$ \frac{-1}{ slope } $, $ Node $, $ \mathcal{C}_w $}
        \State $ sideLine_1 = $ \Call{DerivePoint}{$ slope $, $ pLine.a $, $ \mathcal{C}_l $, $ True $}
        \State $ sideLine_2 = $ \Call{DerivePoint}{$ slope $, $ pLine.b $, $ \mathcal{C}_l $, $ True $}
        \State $ corridor \gets
            \begin{bmatrix}
                pLine.a &
                pLine.b \\

                sideLine_1.a &
                sideLine_2.b \\
            \end{bmatrix} $

        \For{$ node^i $ inside $ corridor $}
            \State $ destination = $ \Call{DerivePoint}{$ \frac{-1}{ slope } $, $ node^i $, $ \mathcal{D} $}

            \State MoveNode ($ node^i, destination.b $)
        \EndFor

        \item[]

        \Procedure{DerivePoint}{$ Slope, Point, Length, IsSideLine $}

        \State init. $ a $, $ b $
        \Switch{$Slope$}
            \Case{$0$}
                \If{$ IsSideLine = True $}
                    \State $ a.x \gets Point.x $
                \Else
                    \State $ a.x \gets Point.x + Length $
                \EndIf
                \State $ a.y \gets Point.y $
                \State $ b.x \gets Point.x - Length $,~$ b.y \gets Point.y $
            \EndCase
            \Case{$ \infty $ or $ -\infty $}
                \State $ a.x \gets Point.x $

                \If{$ IsSideLine = True $}
                    \State $ a.y \gets Point.y $
                \Else
                    \State $ a.y \gets Point.y + Length $
                \EndIf

                \State $ b.x \gets Point.x $,~$ b.y \gets Point.y - Length $
            \EndCase
            \Default
                \State $ dx = \sqrt{\frac{Length}{{1+Slope^2}}}$,~ $ dy = Slope \cdot dx $
                \If{$ IsSideLine = True $}
                    \State $ a.x \gets Point.x $,~$ a.y \gets Point.y $
                \Else
                    \State $ a.x \gets Point.x + dx $,~$ a.y \gets Point.y + dy $
                \EndIf

                \State $ b.x \gets Point.x - dx $,~$ b.y \gets Point.y - dy $
            \EndDefault

        \EndSwitch

        \State \Return{$ a, b $}

@@

>>>>

\section{Cartograms with Dynamic Features}

{
\begin{figure}[b!]
    \centering
    \includegraphics[width=\columnwidth]{example-image-a}
    \caption{An overview of \software. Figure TBA.}
    \label{fig:overview}
\end{figure}
}

\algoref{alg:UpdateNodePosition} provides an overview of our algorithm. We first load and render the CCG geospatial boundaries. For each CCG we compute the centroid and represent it using a square node with $ s $ as its size. We then apply the Fast Node Overlap Removal (VPSC) algorithm \cite{dwyer2006fast} repeatedly to remove overlaps. We chose VPSC over other node overlap removal algorithms since VPSC is able to provide spread minimization and node movement minimization while maintaining a good level of global shape preservation \cite{chen2020Node}. During each iteration, we compute node trajectories (See \algoref{alg:check river crossing}) and translate nodes to their new position. Nodes that cross a river are translated back to their previous position. This procedure ends when 1) no overlaps are present; 2) no nodes cross a river. We then increase $ \nodeSize $ by one pixel and repeat the algorithm until the max node size $ \nodeSizeMax $ is reached.

@@

\begin{algorithm}[tb!]
    \caption{Procedure to update node positions by removing overlap and prevent nodes from crossing rivers.}\label{alg:UpdateNodePosition}
    \textbf{Global variables:} \\
    $ \nodeList \gets $ a list of nodes representing CCGs \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \stalemate \gets $ the maximum number of iterations indicating a stalemate \\

    \textbf{Local variables:} \\
    $ \nodeListVPSC \gets $ a list of nodes representing CCGs after running VPSC \\
    $ \crossRiver \gets $ boolean indicating a node crossed a river \\

    \begin{algorithmic}[1]
        \Procedure{UpdateNodePosition}{}
        \While{$ \nodeSize < \nodeSizeMax $}

        \State $ \nodeListVPSC \gets $ RunVPSC ($ \nodeList $)

            \ForEach {$ \nodeListVPSCEach \in \nodeListVPSC $}

                \If {TranslateNode ($ \nodeListEach, \nodeListVPSCEach $)}
                    \State $ \crossRiver \gets $ \Call{TestRiverCross}{$ \nodeListEach, \nodeListVPSCEach $}

                    \If{$ \crossRiver = True $}
                        \State $ \stalemate \gets \stalemate + 1 $

                        \If{$ \stalemate < \stalemate $}
                            \State \Call{TranslateNode}{$ \nodeListEach $}
                        \Else
                            \State \Call{DeriveCorridor}{$ \nodeListEach, \nodeListVPSCEach $}
                        \EndIf

@@

        \State $ \nodeSize \gets \nodeSize ++$

@@

\begin{algorithm}[tb!]
    \caption{Procedure to update a single node, $ \node $'s position.}\label{alg:move position}

    \textbf{Input:} \\
    $ \node \gets $ required, the node \\
    $ \nodeVPSC \gets $ optional, the node after running VPSC \\

    \textbf{Output:} \\
    A boolean for whether the node's position is updated. \\

    \begin{algorithmic}[1]
        \Procedure{TranslateNode}{$ \node, \nodeVPSC $}
        \If{$ \node.x = \nodeVPSC.x $ and $ \node.y = \nodeVPSC.y $}
            \item[] \Comment{Node position remains unchanged}
            \State \Return{$ False $}
        \EndIf

        \If{$ \nodeVPSC$ is undefined } 
        \item[] \Comment{When optional parameter $ \nodeVPSC $ is undefined}
        \item[] \Comment{Move the node back to its previous position}
            \State $ \node.x \gets \node.previous.x,~\node.y \gets \node.previous.y $
        \Else
            \State $ \node.x \gets \nodeVPSC.x,~\node.y \gets \nodeVPSC.y $
            \State $ \node.history.push(\node.x, \node.y) $
        \EndIf
        \State \Return{$ True $}
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

@@

\subsection{River Cross Testing}

We use rivers as topological boundaries and prevent nodes from crossing them. When a node's position changes, we test if the node's trajectory intersects any segment of a river. See \algoref{alg:check river crossing}. A bounding box intersection test can be performed to reduce the number of edge intersection detections required.

% \begin{noindent}
\begin{algorithm}[tb!]
    \caption{Procedure to test if a node crosses a river.}\label{alg:check river crossing}
    \textbf{Input:} \\
    $ \node \gets $ required, the node \\
    $ \nodeVPSC \gets $ required, the node after running VPSC \\

    \textbf{Output:} \\
    A boolean indicating the node crosses a river. \\

    \textbf{Global variables:} \\
    $ \riverEdgeList \gets $ a list of river edges \\

    \textbf{Local variables:} \\
    $ \riverEdgeListEach \gets $ a river edge in $ \riverEdgeList $ \\ 
    $ \nodeBoundingBox, \riverEdgeBoundingBoxEach \gets $ the bounding boxes for $ \node $ and $ \riverEdgeListEach $ \\
    $ \boundingBoxInt \gets $ boolean indicating $ \nodeBoundingBox $ intersects $ \riverEdgeBoundingBoxEach $ \\
    $ \nodeEdge \gets $ the edge for $ \node $\\
    $ \edgeBoxInt \gets $ boolean indicating $ \nodeEdge $ intersects $ \riverEdgeListEach $ \\

    \begin{algorithmic}[1]
        \Procedure{TestRiverCross}{$ \node, \nodeVPSC $}

        \ForEach{$ \riverEdgeListEach \in \riverEdgeList $}
            \State $ \nodeBoundingBox \gets $ GenerateBoundingBox ($ \node, \nodeVPSC $)
            \State $ \riverEdgeBoundingBoxEach \gets $ GenerateBoundingBox ($ \riverEdgeListEach $)
            \State $ \boundingBoxInt \gets $ TestBoundingIntersection ($ \nodeBoundingBox, \riverEdgeBoundingBoxEach $)

            \If{$ \boundingBoxInt = True $}
                \State $ e_{n} \gets $ GenerateEdge ($ \node, \nodeVPSC $)
                \State $ \edgeBoxInt \gets $ TestEdgeIntersection ($ \nodeEdge, \riverEdgeListEach $)

                \If{$ \edgeBoxInt = True $}
                    \State \Return{$ True $}
                \EndIf

                \EndIf
        \EndFor

        \State \Return{$ False $}
        \EndProcedure
    \end{algorithmic}
\end{algorithm}
%\end{noindent}

@@

As the VPSC always tries to produce an optimal node layout where node distribution and translation are minimized, a node might be repeatedly translated between two positions due to river crossing and congestion, creating a stalemate situation, as shown in \figref{fig:stalemate}. In order to create space for VPSC to generate a new layout, we introduce a parameter, $ \stalemate $, to test for stalemate. If a node is translated between two positions for more than $ \stalemate $ iterations, it is considered to be in a stalemate. A stalemate triggers a corridor derivation which moves all nodes within the corridor by $ d $ set by the user (See \figref{fig:corridor} and \algoref{alg:derive corridor}).

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/stalemate.png}
    \caption{A stalemate situation is when a node repeatedly translates between two positions (A and B) for more than $ stalemate $ iterations. }
    \label{fig:stalemate}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/corridor.png}
    \caption{When a stalemate occurs, a corridor (black rectangular) is derived based on the current (A) and previous (B) positions of the node that crossed a river, as described in \algoref{alg:derive corridor}. All nodes within the corridor are moved by $ d $ in the direction of $ \Vector{B}{A} $. }
    \label{fig:corridor}
\end{figure}
}

@@

\begin{algorithm}[tb!]
    \caption{Procedure to derive a corridor to translate enclosed nodes. We use an SVG canvas, where the point of origin (0,0) is located at the top left corner, with the x-axis extending to the right and the y-axis extending downwards.}\label{alg:derive corridor}

    \textbf{Input:} \\
    $ \node \gets $ the node used to derive the corridor \\

    \textbf{Global variables:} \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \CorridorLength \gets $ the length of a corridor \\
    $ \CorridorWidth \gets $ the width of a corridor \\

    \textbf{Local variables:} \\
    $ \PointP \gets $ the point extending $ \Vector{\node.previous}{~\node} $ such that the length of $ \Vector{\node.previous}{~\PointP} $ is $ \CorridorLength $\\
    $ \EdgeParallelA, \EdgeParallelB \gets $ the edges parallel to $ \Vector{\node}{\PointP} $ \\
    $ corridor \gets $ a rectangular formed by $ \EdgeParallelA $ and $ \EdgeParallelB $ \\

    \begin{algorithmic}[1]
        \Procedure{DeriveCorridor}{$ \node $}
            \State TranslateNode ($ \node $)

            \State $ \PointP \gets $ \Call{DerivePoint}{$ \Vector{\node.previous}{~\node} $, $ \CorridorLength $}

            \State $ \EdgeParallelA \gets $ \Call{DeriveParallelEdge}{$ \Vector{\node.previous}{~\PointP} $, $ \frac{\CorridorWidth}{2} $}

            \State $ \EdgeParallelB \gets $ \Call{DeriveParallelEdge}{$ \Vector{\node.previous}{~\PointP} $, $ -\frac{\CorridorWidth}{2} $}

            \State $ corridor \gets
                \begin{bmatrix}
                    \EdgeParallelA.start &
                    \EdgeParallelA.end \\

                    \EdgeParallelB.start &
                    \EdgeParallelB.end \\
                \end{bmatrix} $

            \ForEach{$ \nodeInCorridorEach $ inside $ corridor $}
                \State $ \nodeInCorridorEachDx \gets \nodeInCorridorEach.x - \nodeInCorridorEach.previous.x $

                \State $ \nodeInCorridorEachDy \gets \nodeInCorridorEach.y - \nodeInCorridorEach.previous.y $

                \State $ hyp \gets \sqrt{(\nodeInCorridorEachDx)^2 +(\nodeInCorridorEachDy)^2} $

                \State $ \nodeInCorridorEach.next \gets $ \Call{DerivePoint}{$ \Vector{\nodeInCorridorEach.previous}{~\nodeInCorridorEach} $, $ hyp + s $}

                \State TranslateNode ($ \nodeInCorridorEach $, $ \nodeInCorridorEach.next $)

            \EndFor
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

    \begin{algorithm}[tb!]
        \caption{Procedure to derive a point based an edge and a distance.}\label{alg:derive corridor point}
        \textbf{Input:} \\
        $ \Edge \gets $ the edge used to derive the new point \\
        $ \Distance \gets $ the distance between $ \PointP $ and $ \Edge.start $ \\

        \textbf{Output:} \\
        A point, $ \PointP $, that is distance $ \Distance $ away from $ \Edge.start $. \\

        \textbf{Local variables:} \\
        $ \dx, \dy \gets $ the differences in $ x, y $ for $ \Edge.start $ and $ \Edge.end $ \\

        \begin{algorithmic}[1]
            \Procedure{DerivePoint}{$ \Edge $, $ \Distance $}
                \State $ \dx \gets \Edge.start.x - \Edge.end.x $

                \State $ \dy \gets \Edge.start.y - \Edge.end.y $

                \State $ \PointP.x \gets \frac{\dx}{\sqrt{\dx^2 + \dy^2}} \cdot \Distance $

                \State $ \PointP.y \gets \frac{\dy}{\sqrt{\dx^2 + \dy^2}} \cdot \Distance $

            \State \Return{$ \PointP $}

@@

\begin{algorithm}[tb!]
    \caption{Procedure to derive an edge, $ \EdgeParallel $, that is parallel to $ \Edge $ with a distance of $ \Distance $.}\label{alg:derive corridor edge}

    \textbf{Input:} \\
    $ \Edge \gets $ the edge used to derive the parallel edge $ \EdgeParallel $ \\
    $ \Distance \gets $ the distance between $ \Edge $ and $ \EdgeParallel $ \\

    \textbf{Output:} \\
    An edge, $ \EdgeParallel $, that is parallel to $ \Edge $ with a distance of $ \Distance $. \\

    \textbf{Local variables:} \\
    $ \dx, \dy \gets $ the differences in $ x, y $ for $ \Edge.start $ and $ \Edge.end $ \\
    $ \Scale \gets $ the scale of $ \frac{\Distance}{\sqrt{\dx^2 + \dy^2}} $ \\

    \begin{algorithmic}[1]
        \Procedure{DeriveParallelEdge}{$ \Edge $, $ \Distance $}
            \State $ \dx \gets \Edge.start.x - \Edge.end.x $

            \State $ \dy \gets \Edge.start.y - \Edge.end.y $

            \State $ \Scale \gets \frac{\Distance}{\sqrt{\dx^2 + \dy^2}} $

            \State $ \EdgeParallel.start.x \gets \Scale \cdot -\dy + \Edge.start.x $

            \State $ \EdgeParallel.start.y \gets \Scale \cdot \dx + \Edge.start.y $

            \State $ \EdgeParallel.end.x \gets \Scale \cdot -\dy + \Edge.end.x $

            \State $ \EdgeParallel.end.y \gets \Scale \cdot \dx + \Edge.end.y $

        \State \Return{$ \EdgeParallel $}
